Density-dependent selection in evolutionary genetics: a lottery model of Grime's triangle

### 2017-04-04 manuscript.tex
latest

\section*{•}

@@

>>>>

\section*{Selection under cyclical population density}

We now consider the situation when both selection and population density cycle periodically. For example, natural \textit{Drosophila} populations undergo seasonal density cycles, expanding rapidly in the warmer months when fruit is abundant, and being carried through the colder months by a much smaller number of dormant individuals. Within these density cycles, allele frequencies also cycle \citep{bergland_14}, and may potentially have been doing so for a long period of time [how many loci, how long].

Figure \ref{fluctuatingselection} shows the behavior of Eq. \eqref{eq:master} for an example where $b$ and $d$ cycle between zero and positive values (``summers'' with rapid growth and no mortality, and ``winters'' with positive mortality and no growth). Selection alternatively favors the $b$ specialist

@@

\begin{figure}
\centering
\includegraphics[scale=0.7]{fluctuatingselection.pdf}
\caption{\label{fig:fluctuatingselection} Stable coexistence between $b$ and $d$ specialists when $b$ and $d$ cycle seasonally. (a) $b$ (solid lines) and $d$ (dashed lines) alternate between  zero and positive. The $b$ specialist (black) has higher $b$ and $d$ than the $d$ specialist. (b) Both types increase in abundance during the positive $b$ phase, and decline during the positive $d$ phase, but the $d$ specialist (blue area) does so at a slower rate than the $b$ specialist (black area). Total area (blue+black) shows the cycles in total population size $N$. (c) The positive $b$ and $d$ phases favor the $b$ and $d$ specialists, respectively. However, due to the storage effect neither has an advantage over a full environemntal cycle, and they stably coexist.} 
\end{figure}
